Title

### 2025-02-05 index.qmd
changed how results organized

```{r setup, include = FALSE}
library(tidyverse)
library(kableExtra)  # For collapse_rows() to work: https://stackoverflow.com/a/67803915/6373540
library(tools)

results_dir <- file.path('.', 'results')
graphs_dir <- file.path(results_dir, 'graphs')

metros <- c(
  'atlanta',
  'bay area',
  'boston',
  'chicago',
  'cleveland',
  'dallas',
  'dc maryland virginia',
  'detroit',
  'houston',
  'long island',
  'los angeles',
  'miami',
  'new york city',
  'northern new jersey',
  'orange county',
  'philadelphia',
  'san diego'
)

rqs <- c('rq1', 'rq2')
graph_types <- c('race', 'ses')
```

@@

```{r, echo=FALSE, results='asis'}
insert_figure <- function(rq, metro, graph_type, base_path = graphs_dir) {
  metro <- str_replace_all(string = metro, pattern = ' ', replacement = '_')

  fig_file <- file.path(base_path, str_c(rq, '_', metro, '_', graph_type, '.png'))
  cap_file <- file.path(base_path, str_c(rq, '_', metro, '_', graph_type, '_title.txt'))
  note_file <- file.path(base_path, str_c(rq, '_', metro, '_', graph_type, '_note.txt'))

  # Print caption
  writeLines(paste0('#### ', readLines(cap_file, warn = F)))

  # Output the figure block to the doc
  writeLines(paste0('![](', fig_file, ')\n'))

  # Print footnotes
  writeLines(paste0('<div class="footnote">', paste0(readLines(note_file, warn = F), collapse = '</br>'), '</div>'))
}

for (m in metros) {

  # Print a top-level heading for the metro area
  writeLines(paste0('## ', toTitleCase(m), ' area'))

  for (rq in rqs) {
    rq_num <- str_replace(string = rq, pattern = 'rq', replacement = '')

    if (rq == 'rq1') { # rq1 run for every metro area

      for (g in graph_types) {

        # Print a heading for the RQ
        writeLines(paste0('### Research question ', rq_num))

        insert_figure(metro = m, rq = rq, graph_type = g)
      }

    } else if (rq == 'rq2' & (m %in% c('chicago','philadelphia'))) { # rq2 run only for specific metro areas and orders

      # Separate rq2 graphs for race and for firstgen status; they apply to all above metro areas
      for (suffix in c('race_row_plot', 'race_col_plot', 'firstgen_row_plot', 'firstgen_col_plot')) {

        # Print a heading for the RQ
        writeLines(paste0('### Research question ', rq_num))

        insert_figure(metro = m, rq = rq, graph_type = suffix)

      }

      if (m == 'chicago') {

        # Print a heading for the RQ
        writeLines(paste0('### Research question ', rq_num))

        insert_figure(metro = m, rq = rq, graph_type = 'order_487984_race_by_firstgen')

        # Print a heading for the RQ
        writeLines(paste0('### Research question ', rq_num))

        insert_figure(metro = m, rq = rq, graph_type = 'order_488035_488053_race_by_firstgen')

      } else if (m == 'philadelphia') {

        # Print a heading for the RQ
        writeLines(paste0('### Research question ', rq_num))

        insert_figure(metro = m, rq = rq, graph_type = 'order_448922_race_by_firstgen')

        # Print a heading for the RQ
        writeLines(paste0('### Research question ', rq_num))

        insert_figure(metro = m, rq = rq, graph_type = 'order_448427_448440_race_by_firstgen')

      }
    }
  }
}
```

>>>>

@@

```{r setup, echo=FALSE, results = 'asis'}
```{r, echo=FALSE, results='asis'}
library(tidyverse)
library(kableExtra)  # For collapse_rows() to work
library(tools)

# Example directories
graphs_dir <- file.path(".", "results", "graphs")

# 1) Define the `insert_figure` helper function
insert_figure <- function(rq, metro, graph_type, base_path = graphs_dir) {

  # Convert spaces -> underscores for filenames
  metro_underscored <- str_replace_all(metro, " ", "_")

  # Build the three file paths (PNG, title TXT, note TXT)
  fig_file  <- file.path(base_path, rq, str_c(rq, "_", metro_underscored, "_", graph_type, ".png"))
  cap_file  <- file.path(base_path, rq, str_c(rq, "_", metro_underscored, "_", graph_type, "_title.txt"))
  note_file <- file.path(base_path, rq, str_c(rq, "_", metro_underscored, "_", graph_type, "_note.txt"))

  # Print a heading / caption
  caption_text <- if (file.exists(cap_file)) readLines(cap_file, warn = FALSE) else "No Title Found"
  writeLines(paste0("#### ", caption_text))

  # Output the figure (if it exists)
  if (file.exists(fig_file)) {
    writeLines(str_c("![](", fig_file, ")\n"))
  } else {
    writeLines(paste("*(Missing figure file:", fig_file, ")*\n"))
  }

  # Print footnotes (if the .txt file exists)
  if (file.exists(note_file)) {
    notes_txt <- readLines(note_file, warn = FALSE)
    writeLines(
      str_c(
        "<div class=\"footnote\">",
        paste0(notes_txt, collapse = "</br>"),
        "</div>"
      )
    )
  }
}

# 2) Define your metros / RQs
metros <- c(
  "atlanta",
  "bay area",
  "boston",
  "chicago",
  "cleveland",
  "dallas",
  "dc maryland virginia",
  "detroit",
  "houston",
  "long island",
  "los angeles",
  "miami",
  "new york city",
  "northern new jersey",
  "orange county",
  "philadelphia",
  "san diego"
)

rqs <- c("rq1", "rq2")

# For RQ1, we have two plot types: "race" and "ses"
graph_types_rq1 <- c("race", "ses")

# 3) Subset of metros with RQ2 data (2 orders each)
rq2_metros <- c(
  "chicago", "philadelphia", "los angeles", 
  "orange county", "san diego", "bay area",
  "northern new jersey"
)

# We'll define a "metro_orders" list for those RQ2 metros:
metro_orders <- list(
  "chicago"             = c("487984", "488035_488053"),
  "philadelphia"        = c("448922", "448427_448440"),
  "northern_new_jersey" = c("448922", "448427_448440"),
  "los_angeles"         = c("448375", "448374_448420"),
  "orange_county"       = c("448375", "448374_448420"),
  "san_diego"           = c("448375", "448374_448420"),
  "bay_area"            = c("448375", "448374_448420")
)

# 4) Main loop
for (m in metros) {

  # Print a top-level heading for the metro area
  writeLines(str_c("## ", tools::toTitleCase(m), " area"))

  for (rq in rqs) {

    # For clarity, parse out the numeric portion
    rq_num <- str_replace(string = rq, pattern = "rq", replacement = "")

    # ---------------------------------------------
    # RQ1 Logic
    # ---------------------------------------------
    if (rq == "rq1") {

      # Each metro has 2 plots: "race" & "ses"
      for (g in graph_types_rq1) {
        writeLines(str_c("### Research question ", rq_num))
        insert_figure(rq = rq, metro = m, graph_type = g)
      }

    # ---------------------------------------------
    # RQ2 Logic (row vs. col approach)
    # ---------------------------------------------
    } else if (rq == "rq2") {

      # Only run RQ2 code if the metro is in our RQ2 list
      if (!(m %in% rq2_metros)) next

      # Convert name -> underscores for matching list keys
      m_underscored <- str_replace_all(m, " ", "_")
      orders_for_m  <- metro_orders[[m_underscored]]

      # If a metro isn't in the list or no orders, skip
      if (is.null(orders_for_m)) next

      # We'll do 2 group types: race & firstgen
      for (g in c("race", "firstgen")) {

        # We'll do row and col for each group type
        for (rc in c("row", "col")) {

          if (rc == "row") {
            #
            # ROW => single combined figure on one slide
            #
            writeLines(str_c("### Research question ", rq_num))
            graph_type_row <- str_c(g, "_", rc, "_plot")
            insert_figure(rq = rq, metro = m, graph_type = graph_type_row)

          } else {
            #
            # COL => separate file(s) by order ID => each on its own slide
            #
            for (order_id in orders_for_m) {

              # Each order ID gets its own "###" => new Reveal.js slide
              writeLines(str_c("### Research question ", rq_num))

              # e.g. "rq2_chicago_race_col_plot_487984.png"
              graph_type_col <- str_c(g, "_", rc, "_plot_", order_id)
              insert_figure(rq = rq, metro = m, graph_type = graph_type_col)
            }

          } # end if row vs col

        } # end rc loop

      } # end g loop

    } # end if (rq == "rq2")

  } # end rq loop

} # end metros loop

```
